---
title: "p8105_hw5_pz2281"
author: "Peilin Zhou"
output: github_document
---

```{r, message = FALSE}
library(tidyverse)
library(ggplot2)
```

## Problem 1

Import and clean the data
```{r, message = FALSE}
homicides_data = read_csv(file = "./data/homicide-data.csv", na = c("", "Unknown"))
head(homicides_data) 
```
The raw data contained homicides cases from 50 large U.S. cities. Variables include unique case id of each city from an ascending order, reported date of the case, victim's name, race, age, sex, where the case happened specified in geographical coordinates and name of hte city/state, and case disposition. There are `r nrow(homicides_data)` observations and `r ncol(homicides_data)` variables. Missing values exist in victim_race, victim_age, victim_race, and geographical coordindates. Missing values were changed to N/A. We see that there is one possible data entry error which city Tulsa should be in state Oklahoma instead of Alabama. To make consistency for later analysis, omit this one oberservation.

add new variables to the data frame and do summarization with conditions
```{r}
homicides_data = homicides_data %>% 
  mutate(
    city_state = str_c(city,state, sep = ",")
  ) %>% 
  filter(city_state != "Tulsa,AL") %>% 
  relocate(city_state)

#total number of homicides within cities
homicides_data %>% 
  group_by(city_state) %>% 
  summarise(
    n = n()
  ) %>% knitr::kable()
```
Total number of homicide cases within each city as a table.

```{r}
#total number of unsolved homicides
homicides_data  = homicides_data %>% 
  mutate(status = ifelse(disposition == "Closed by arrest", "solved", "unsolved")) 

unsolved_table = homicides_data %>% 
  filter(status == "unsolved") %>% 
  group_by(city_state) %>% 
  summarise(unsolved_case = n()) %>% 
  knitr::kable()
unsolved_table
```
Total number of unsolved homicide cases within each city as a table.

Conduct prop.test for Baltimore,MD
```{r}
bal_unsolved_data = homicides_data %>% 
  filter(city_state == "Baltimore,MD") %>% 
  summarise(
    unsolved = sum(status == "unsolved"),
    num_case = n()
  ) 

bal_test_result = 
  prop.test(x = bal_unsolved_data %>% pull(unsolved), n = bal_unsolved_data %>% pull(num_case)) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)
bal_test_result
```
The estimated proportion of unsolved homicides in Baltimore is `r bal_test_result$estimate`. The 95% confidence interval is `r bal_test_result$conf.low` to `r bal_test_result$conf.high`.

prop.test for every city:

First, write a function to make the above steps generalized to every dataframe with same variable/format
```{r}
city_test = function(df) {
  df_test = df %>% 
    summarise(
    unsolved = sum(status == "unsolved"),
    num_case = n()
  ) 

city_test_result = prop.test(x = df_test %>% pull(unsolved), n = df_test %>% pull(num_case)) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)

return(city_test_result)
}
```

Calling the function by mapping for the nested df and unnest it for better illustration of the results.
```{r}
homicides_nest_result = 
  homicides_data %>% 
  nest(data = uid:status) %>% 
  mutate(test_result = map(data, city_test)) %>% 
  unnest(test_result) %>% 
  select(-data)

homicides_nest_result %>% 
  knitr::kable()
```

Plot the confidence interval and estimated proportion:
```{r}
homicides_nest_result %>% 
  mutate(city_state = forcats::fct_reorder(city_state, estimate)) %>%
  ggplot() +
  geom_errorbar(mapping = aes(x = city_state, ymin = conf.low, ymax = conf.high)) +
  geom_point(mapping = aes(x = city_state, y = estimate)) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    title = "95% Confidence interval and Estimated Proportion \n of Unsolved Homicides Cases in Each City",
    x = "City",
    y = "Proportion"
       )
```

## Problem 2

```{r}
path = "./data/data2"
data_names = list.files(path, pattern = ".csv")
```


```{r, message = FALSE}
study_df = tibble(
  id = data_names
) %>% 
  mutate(vars = map(id, ~ read_csv(file.path(path, .)))) %>% 
  unnest(vars) %>% 
  pivot_longer(
    cols = !id,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observed_value"
    ) %>% 
  mutate(id = gsub(".csv", "", id)) %>% 
  mutate(arm_id = id) %>% 
  separate(id, c("arm", "id"), sep = "_") %>% 
  mutate(arm = recode(arm, con = "control", exp = "experimental"))
study_df
```

dataframe was cleaned.

```{r, message = FALSE}
spaghetti_plot = study_df %>% 
  ggplot(aes(x = week, y = observed_value, group = arm_id, color = arm)) +
  geom_line(alpha = 0.5) +
  labs(
    title = "Change of Observed Values by Week \n for Each Subject in Different Arms",
    x = "Week",
    y = "Observed Values"
  )
spaghetti_plot
```

From the plot, we can see that from week 1 to week 8, there was an noticeable trend of general increase of the observed value in the experimental group. The change of the value is from around 0-3.75 to 3.75-7. However, there is no significant trend of increase or decrease for the observed value in the control group as weeks passed. Observed values maintained around 0 to 2.5 from week 1 to week 8.

## Problem 3

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Write function:
```{r}
missing_values_handle = function(x) {
   if (!is.numeric(x)) {
    x = ifelse(is.na(x), "virginica", x)
  } else {
    x = ifelse(is.na(x), mean(x, na.rm = TRUE), x)
  }
  return(x)
}
```

passing it to the data by mapping
```{r}
iris_list_missing  = as.list(iris_with_missing)
iris_no_NA =  map(.x = iris_list_missing, ~ missing_values_handle(.x)) %>% 
 bind_rows()
iris_no_NA

#show there is no missing values
iris_no_NA %>%
  summarise_all(~ sum(is.na(.)))
```

Numerical missing values are replaced with mean of non-missing values for each variable. Missing values in character variables are replaced with 'verginica'.




